Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2015-07-13 Papers/InProgress/HajekAndersonControversy/main.tex
Add summary table to paper

>>>>

Figure \ref{fig:summary} summarizes the results obtained by the automated reasoning tools. The following abbreviations are used: S/I = superfluous and independent; R = superfluous and redundant; S/U = superfluous and unknown whether redundant or independent; N/I = non-superfluous and independent; P = provable; CS = counter-satisfiable. The weakest logic required to show redundancy or provability is indicated in parentheses (\K is the default). 
Cells highlighted in red contain results that differ from what had been claimed by either Magari, Anderson or Hájek. Cells highlighted in yellow contain results that are surprising, albeit not contradicting any claims. Cells highlighted in green contain results where the tools were able to obtain the same results as humans, but using weaker modal logics.

\begin{figure}
\includegraphics[width=\textwidth]{Summary.png}
\caption{Summary of Results}
\label{fig:summary}
\end{figure}
